---
title: "analysis_plots"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(glue)
library(ggpubr)
library(stringr)
library(RColorBrewer)

theme_set(theme_bw(base_size = 16,
  base_family = "Times New Roman"))
```

# Plots for VQA function word analyses

## Experiment 1 : Trained on CLEVR

```{r}
# For experiment 1 run 0
result_dir0 = "../../data/results/2022-03-06_experiment1_e25_4mac_newANDORonly_seed0"
result_dir1 = "../../data/results/2022-03-06_experiment1_e25_4mac_newANDORonly_seed1"
result_dir2 = "../../data/results/2022-03-06_experiment1_e25_4mac_newANDORonly_seed2"
result_dir3 = "../../data/results/2022-03-06_experiment1_e25_4mac_newANDORonly_seed3"
result_dir4 = "../../data/results/2022-03-06_experiment1_e25_4mac_newANDORonly_seed4"

result_dirs = c(result_dir0, result_dir1, result_dir2, result_dir3, result_dir4)
```

## Experiment 1 Appendix : Using old SAME probe
```{r}
# For experiment 1 run 0
result_dir0 = "../../data/results/2022-02-01_epochprobes_e25_4mac_newh5"
result_dir1 = "../../data/results/2022-02-04_epochprobes_e25_4mac_newh5_seed1"
result_dir2 = "../../data/results/2022-02-07_epochprobes_e25_4mac_newh5_seed2"

result_dirs = c(result_dir0, result_dir1, result_dir2)
```


## Experiment 2 : Trained on subsampled CLEVR with childes frequencies
```{r}
# For experiment 1 run 0
result_dir0 = "../../data/results/2022-03-16_experiment2_e25_4mac_newANDORonly_seed0"
result_dir1 = "../../data/results/2022-03-16_experiment2_e25_4mac_newANDORonly_seed1"
result_dir2 = "../../data/results/2022-03-16_experiment2_e25_4mac_newANDORonly_seed2"
result_dir3 = "../../data/results/2022-03-16_experiment2_e25_4mac_newANDORonly_seed3"
result_dir4 = "../../data/results/2022-03-16_experiment2_e25_4mac_newANDORonly_seed4"

result_dirs = c(result_dir0, result_dir1, result_dir2, result_dir3, result_dir4)
```


## Experiment 3 : Trained on no AND no EQUAL version of CLEVR

```{r}
# For experiment 1 run 0
result_dir0 = "../../data/results/2022-03-11_experiment3_e25_4mac_newANDORonly_seed0"
result_dir1 = "../../data/results/2022-03-11_experiment3_e25_4mac_newANDORonly_seed1"
result_dir2 = "../../data/results/2022-03-11_experiment3_e25_4mac_newANDORonly_seed2"
result_dir3 = "../../data/results/2022-03-11_experiment3_e25_4mac_newANDORonly_seed3"
result_dir4 = "../../data/results/2022-03-11_experiment3_e25_4mac_newANDORonly_seed4"

result_dirs = c(result_dir0, result_dir1, result_dir2, result_dir3, result_dir4)
```

### AND2 and MORE/LESS without or
```{r}
# For experiment 1 run 0
result_dir0 = "../../data/results/2022-03-20_experiment3noor_e25_4mac_seed0"
result_dir1 = "../../data/results/2022-03-20_experiment3noor_e25_4mac_seed1"
result_dir2 = "../../data/results/2022-03-20_experiment3noor_e25_4mac_seed2"
result_dir3 = "../../data/results/2022-03-20_experiment3noor_e25_4mac_seed3"
result_dir4 = "../../data/results/2022-03-20_experiment3noor_e25_4mac_seed4"

result_dirs = c(result_dir0, result_dir1, result_dir2, result_dir3, result_dir4)
```

### Overall accuracy during learning

Note that the overall accuracy of ORprobe is lower than it should be since ambiguous questions are included here.
```{r}
get_overall_acc <- function(result_dir){
  expname = str_split(result_dir, "../../data/results/")[[1]][2]
  seed = as.integer(str_sub(expname, -1, -1))
  filename = paste(result_dir, "/probe-results-", expname, ".csv", sep="")
  overall_acc <- read_csv(filename, skip=1)
  overall_acc <- overall_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |>
  pivot_longer(cols = c(ANDprobeAcc, ORprobeAcc, MOREprobeAcc, LESSprobeAcc, BEHINDprobeAcc, FRONTprobeAcc, SAMEprobeAcc), names_to="probetype", values_to="acc") |>
    mutate(seed = seed)
  return(overall_acc)
}

overall_res <- result_dirs |> map(get_overall_acc) |> reduce(rbind)

mean_overall_res <- overall_res |>
  group_by(probetype, epoch, batches, batchNum) |>
  summarise(mean_acc = mean(acc), sd_acc = sd(acc))

mean_overall_res_epochs <- mean_overall_res |> filter(batchNum == 0)

ggplot(mean_overall_res_epochs, aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = mean_acc - sd_acc, ymax = mean_acc + sd_acc, fill= probetype), alpha=0.3) +
  geom_line(aes(color=probetype))

ggplot(mean_overall_res_epochs |> filter(probetype %in% c("ANDprobeAcc", "ORprobeAcc")), aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = mean_acc - sd_acc, ymax = mean_acc + sd_acc, fill= probetype), alpha=0.3) +
  geom_line(aes(color=probetype))

ggplot(mean_overall_res_epochs |> filter(probetype %in% c("MOREprobeAcc", "LESSprobeAcc")), aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = mean_acc - sd_acc, ymax = mean_acc + sd_acc, fill= probetype), alpha=0.3) +
  geom_line(aes(color=probetype))

ggplot(mean_overall_res_epochs |> filter(probetype %in% c("BEHINDprobeAcc", "FRONTprobeAcc")), aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = mean_acc - sd_acc, ymax = mean_acc + sd_acc, fill= probetype), alpha=0.3) +
  geom_line(aes(color=probetype))


```

### Analyses by probe type


#### AND2 - OR2 by answer type
```{r}

get_and_or_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  and_filename = paste(result_dir, "probeAND2_res_by_answer_type.csv", sep="/")
  or_filename = paste(result_dir, "probeOR2_res_by_answer_type.csv", sep="/")
  and_acc <- read_csv(and_filename)
  or_acc <- read_csv(or_filename)
  and_or_acc <- rbind(and_acc, or_acc)
  
  and_or_acc <- and_or_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(probetype, epoch, batchNum) |>
    mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(and_or_acc)
}


and_or_res <- result_dirs |> map(get_and_or_acc) |> reduce(rbind)

ggplot(and_or_res, aes(x=epoch, y=overall_correct, color = as.factor(seed)))+
  geom_line(size=1.3) +
  labs(x= "Epoch", y="accuracy", color = "seed", linetype = "Probe type") +
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

mean_and_or_res <- and_or_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))


probe.labs <- c("AND", "OR")
names(probe.labs) <- c("probeAND2", "probeOR2")

p = ggplot(mean_and_or_res, aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_and2_or2_answertype_sd.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
#ggsave("exp2_and2_or2_answertype_sd.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")

p = ggplot(mean_and_or_res |> filter(probetype == "probeOR2"), aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
p


#ggsave("exp3_or2_answertype100.jpeg", plot=p, device="jpeg", width = 5.3, height = 3.5, units="in")


p = ggplot(mean_and_or_res |> filter(probetype == "probeAND2"), aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
p

#ggsave("exp3_and2_answertype100.jpeg", plot=p, device="jpeg", width = 5.3, height = 3.5, units="in")


p = ggplot(mean_and_or_res, aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  scale_color_manual(labels=c("AND", "OR"), values=c("#225ea8", "#cc4c02"))+
  scale_fill_manual(labels=c("AND", "OR"), values=c("#225ea8", "#cc4c02"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
  
p  
#ggsave("exp1_and2_or2_overall100.jpeg", plot=p, device="jpeg", width = 5, height = 3.5, units="in")
ggsave("exp2_and2_or2_overall100.jpeg", plot=p, device="jpeg", width = 5, height = 3.5, units="in")



p = ggplot(mean_and_or_res |> filter(probetype == "probeOR2"), aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  scale_color_manual(labels=c("OR"), values=c("#cc4c02"))+
  scale_fill_manual(labels=c("OR"), values=c("#cc4c02"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
  
p
#ggsave("exp3_or2_overall100.jpeg", plot=p, device="jpeg", width = 5.3, height = 3.5, units="in")

p = ggplot(mean_and_or_res |> filter(probetype == "probeAND2"), aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  scale_color_manual(labels=c("AND"), values=c("#225ea8"))+
  scale_fill_manual(labels=c("AND"), values=c("#225ea8"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
  
p
#ggsave("exp3_and2_overall100.jpeg", plot=p, device="jpeg", width = 5.3, height = 3.5, units="in")

```

```{r}

get_or_amb_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  filename = paste(result_dir, "probeOR2_res_or_inclusive_exclusive.csv", sep="/")
  or_amb_acc <- read_csv(filename)
  
  or_amb_acc <- or_amb_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
  pivot_longer(cols = c(prop_inclusive, prop_exclusive), names_to="answer_type", values_to="proportion") |>
    mutate(seed = seed)
  
  return(or_amb_acc)
}


or_amb_res <- result_dirs |> map(get_or_amb_acc) |> reduce(rbind)

ggplot(or_amb_res |> filter(answer_type == "prop_exclusive"), aes(x=epoch, y=proportion)) + geom_line(aes(color=as.factor(seed)))

mean_or_amb_res <- or_amb_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, answer_type) |>
  summarise(mean_prop = mean(proportion), sd_prop = sd(proportion))

p= ggplot(mean_or_amb_res, aes(x=epoch, y=mean_prop, fill=answer_type)) +
  geom_ribbon(aes(ymin = (mean_prop - sd_prop), ymax = (mean_prop + sd_prop)), alpha=0.3)+
  geom_line(aes(color=answer_type), size=1.3)+
  scale_color_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  scale_fill_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  labs(x= "Epoch", y="Proportion", color = "OR interpretation", fill = "OR interpretation") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))


p= ggplot(mean_or_amb_res |> filter(answer_type == "prop_exclusive"), aes(x=epoch, y=mean_prop, fill=answer_type)) +
  geom_ribbon(aes(ymin = 0, ymax = (mean_prop)), alpha=0.7)+
  #geom_line(aes(color=answer_type), size=1.3)+
  scale_color_manual(labels=c("exclusive"), values=c("#8c6bb1"))+
  scale_fill_manual(labels=c("exclusive"), values=c("#8c6bb1"))+
  ylim(0,0.8)+
  labs(x= "Epoch", y="Proportion", color = "OR interpretation", fill = "OR interpretation") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p

#ggsave("exp1_or2_inclusive_exclusive_sd.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")
#ggsave("exp2_or2_inclusive_exclusive_sd.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")
#ggsave("exp3_or2_inclusive_exclusive_sd.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")

p= ggplot(mean_or_amb_res |> filter(answer_type == "prop_exclusive"), aes(x=epoch, y=mean_prop, fill=answer_type)) +
  geom_ribbon(aes(ymin = 0, ymax = mean_prop), alpha=0.5)+
  geom_hline(yintercept=0.5, linetype="dashed", alpha = 0.6)+
  scale_color_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  scale_fill_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  scale_y_continuous(limits = c(0, 1))+
  labs(x= "Epoch", y="Proportion", color = "OR interpretation", fill = "OR interpretation") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p

#ggsave("exp1_or2_exclusive_sd1.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")
#ggsave("exp2_or2_exclusive_sd1.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")
#ggsave("exp3_or2_exclusive_sd1.jpeg", plot=p, device="jpeg", width = 5.6, height = 3.5, units="in")
```
#### AND2 - OR2 EXPERIMENT 3 Side by side
```{r}
get_and_or_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  and_filename = paste(result_dir, "probeAND2_res_by_answer_type.csv", sep="/")
  or_filename = paste(result_dir, "probeOR2_res_by_answer_type.csv", sep="/")
  and_acc <- read_csv(and_filename)
  or_acc <- read_csv(or_filename)
  and_or_acc <- rbind(and_acc, or_acc)
  
  and_or_acc <- and_or_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(probetype, epoch, batchNum) |>
    mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(and_or_acc)
}

get_or_amb_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  filename = paste(result_dir, "probeOR2_res_or_inclusive_exclusive.csv", sep="/")
  or_amb_acc <- read_csv(filename)
  
  or_amb_acc <- or_amb_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
  pivot_longer(cols = c(prop_inclusive, prop_exclusive), names_to="answer_type", values_to="proportion") |>
    mutate(seed = seed)
  
  return(or_amb_acc)
}


# get experiment 1 data
and_or_res <- result_dirs |> map(get_and_or_acc) |> reduce(rbind)
and_exp1 <- and_or_res |> filter(probetype == "probeAND2")
and_exp1 <- and_exp1 |> mutate(experiment = "With alternative")
or_exp1 <- and_or_res |> filter(probetype == "probeOR2")
or_exp1 <- or_exp1 |> mutate(experiment = "With alternative")

or_amb_res <- result_dirs |> map(get_or_amb_acc) |> reduce(rbind)
or_amb_exp1 <- or_amb_res |> filter(probetype == "probeOR2")
or_amb_exp1 <- or_amb_exp1 |> mutate(experiment = "With alternative")


# then get experiment 3 data OR
and_or_res <- result_dirs |> map(get_and_or_acc) |> reduce(rbind)
or_exp3 <- and_or_res |> filter(probetype == "probeOR2")
or_exp3 <- or_exp3 |> mutate(experiment = "Without alternative")

or_amb_res <- result_dirs |> map(get_or_amb_acc) |> reduce(rbind)
or_amb_exp3 <- or_amb_res |> filter(probetype == "probeOR2")
or_amb_exp3 <- or_amb_exp3 |> mutate(experiment = "Without alternative")

# then get experiment 3 data AND
and_or_res <- result_dirs |> map(get_and_or_acc) |> reduce(rbind)
and_exp3 <- and_or_res |> filter(probetype == "probeAND2")
and_exp3 <- and_exp3 |> mutate(experiment = "Without alternative")

# combine:
comb_results <- rbind(and_exp1, or_exp1, and_exp3, or_exp3)
comb_or_amb <- rbind(or_amb_exp1, or_amb_exp3)

mean_comb_results <- comb_results |> filter(batchNum == 0) |>
  group_by(experiment, probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))

mean_comb_or_amb <- comb_or_amb |> filter(batchNum == 0) |>
  group_by(experiment, probetype, epoch, answer_type) |>
  summarise(mean_prop = mean(proportion), sd_prop = sd(proportion))

probe.labs <- c("AND", "OR")
names(probe.labs) <- c("probeAND2", "probeOR2")

## Comparative plots for AND

p = ggplot(mean_comb_results |> filter(probetype == "probeAND2"), aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  facet_wrap(vars(experiment))+
  scale_color_manual(labels=c("AND"), values=c("#225ea8"))+
  scale_fill_manual(labels=c("AND"), values=c("#225ea8"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
  
p
#ggsave("exp3_and2_overall100_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")

p = ggplot(mean_comb_results |> filter(probetype == "probeAND2"), aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  facet_wrap(vars(experiment))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
p

#ggsave("exp3_and2_answertype100_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")


## Comparative plots for OR

p = ggplot(mean_comb_results |> filter(probetype == "probeOR2"), aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  facet_wrap(vars(experiment))+
  scale_color_manual(labels=c("OR"), values=c("#cc4c02"))+
  scale_fill_manual(labels=c("OR"), values=c("#cc4c02"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
  
p
#ggsave("exp3_or2_overall100_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")

p = ggplot(mean_comb_results |> filter(probetype == "probeOR2"), aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  facet_wrap(vars(experiment))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))
p

#ggsave("exp3_or2_answertype100_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")


p= ggplot(mean_comb_or_amb |> filter(answer_type == "prop_exclusive"), aes(x=epoch, y=mean_prop, fill=answer_type)) +
  geom_ribbon(aes(ymin = 0, ymax = mean_prop), alpha=0.5)+
  facet_wrap(vars(experiment))+
  geom_hline(yintercept=0.5, linetype="dashed", alpha = 0.6)+
  scale_color_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  scale_fill_manual(labels=c("exclusive", "inclusive"), values=c("#8c6bb1", "#41ae76"))+
  scale_y_continuous(limits = c(0, 1))+
  labs(x= "Epoch", y="Proportion", color = "OR interpretation", fill = "OR interpretation") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p

ggsave("exp3_or2_exclusive_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
```

#### BEHIND - FRONT by answer type
```{r}
get_behind_front_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  behind_filename = paste(result_dir, "probeBEHIND_res_by_answer_type.csv", sep="/")
  front_filename = paste(result_dir, "probeFRONT_res_by_answer_type.csv", sep="/")
  behind_acc <- read_csv(behind_filename)
  front_acc <- read_csv(front_filename)
  behind_front_acc <- rbind(behind_acc, front_acc)
  
  behind_front_acc <- behind_front_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
  group_by(probetype, epoch, batchNum) |>
  mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(behind_front_acc)
}

behind_front_res <- result_dirs |> map(get_behind_front_acc) |> reduce(rbind)

mean_behind_front_res <- behind_front_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))



probe.labs <- c("BEHIND", "IN FRONT OF")
names(probe.labs) <- c("probeBEHIND", "probeFRONT")

p= ggplot(mean_behind_front_res, aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))


ggplot(behind_front_res, aes(x=epoch, y=prop_correct))+
  geom_line(aes(color=answer), size = 1.3)+
  facet_grid(rows=vars(seed), cols=vars(probetype))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))


p
#ggsave("exp1_behind_front_answertype100.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
#ggsave("exp2_behind_front_answertype100.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")


p = ggplot(mean_behind_front_res, aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  scale_color_manual(labels=c("BEHIND", "IN FRONT OF"), values=c("#225ea8", "#cc4c02"))+
  scale_fill_manual(labels=c("BEHIND", "IN FRONT OF"), values=c("#225ea8", "#cc4c02"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

ggplot(behind_front_res, aes(x=epoch, y=overall_correct, color = as.factor(seed)))+
  geom_line(size=1.3) +
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  labs(x= "Epoch", y="accuracy", color = "seed", linetype = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_behind_front_overall.jpeg", plot=p, device="jpeg", width = 5.7, height = 3.5, units="in")
#ggsave("exp2_behind_front_overall100.jpeg", plot=p, device="jpeg", width = 5.7, height = 3.5, units="in")

```


#### BEHIND - FRONT by distance
```{r}

get_behind_front_bydist <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  behind_filename = paste(result_dir, "probeBEHIND_res_by_round_dist.csv", sep="/")
  front_filename = paste(result_dir, "probeFRONT_res_by_round_dist.csv", sep="/")
  behind_round_dist <- read_csv(behind_filename)
  front_round_dist <- read_csv(front_filename)
  behind_front_round_dist <- rbind(behind_round_dist, front_round_dist)

  behind_front_round_dist <- behind_front_round_dist |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
  group_by(probetype, epoch, batchNum, batches, dist) |>
  mutate(n_by_dist = sum(counts)) |>
  mutate(correct = ifelse(answer==prediction, "true", "false")) |>
  group_by(probetype, epoch, batchNum, batches, dist, correct) |>
  mutate(n_correct_by_dist = sum(counts))
  
  behind_front_round_dist_sum <- behind_front_round_dist |> 
  filter(correct == "true") |>
  mutate(prop_correct = n_correct_by_dist/n_by_dist) |>
  select(c(probetype, epoch, batches, dist, prop_correct)) |>
  unique() |>
    mutate(seed=seed)
  
  return(behind_front_round_dist_sum)
}

behind_front_dist_res <- result_dirs |> map(get_behind_front_bydist) |> reduce(rbind)

mean_behind_front_dist_res <- behind_front_dist_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, dist) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct))

# by epoch
ggplot(mean_behind_front_dist_res |> filter(epoch > 0), aes(x=epoch, y=mean_acc, color=dist))+
  geom_point() +
  facet_wrap(vars(probetype))

plot_data <- mean_behind_front_dist_res |> filter(epoch > 0) |> 
  mutate(dist = as.factor(dist))

cols <- c("1" = "#08306b", "2" = "#08519c", "3" = "#2171b5", "4" = "#4292c6", "5" = "#6baed6", "6" = "#9ecae1", "7" = "#c6dbef", "8" = "#deebf7")
#"8" = "#deebf7"

p = ggplot(plot_data , aes(x=epoch, y=mean_acc, color=dist))+
  geom_line(size=1.3) +
  scale_color_manual(values=cols)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  labs(x= "Epoch", y="Mean accuracy", color = "Distance", fill = "Distance") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_behind_front_bydistance.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
#ggsave("exp2_behind_front_bydistance.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
  
```


#### MORE - LESS by answer type
```{r}

get_more_less_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  more_filename = paste(result_dir, "probeMORE_res_by_answer_type.csv", sep="/")
  less_filename = paste(result_dir, "probeLESS_res_by_answer_type.csv", sep="/")
  more_acc <- read_csv(more_filename)
  less_acc <- read_csv(less_filename)
  more_less_acc <- rbind(more_acc, less_acc)

  more_less_acc <- more_less_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(probetype, epoch, batchNum) |>
    mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(more_less_acc)
}

more_less_res <- result_dirs |> map(get_more_less_acc) |> reduce(rbind)

mean_more_less_res <- more_less_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))

probe.labs <- c("MORE", "FEWER")
names(probe.labs) <- c("probeMORE", "probeLESS")

ggplot(more_less_res, aes(x=epoch, y=overall_correct, color = as.factor(seed)))+
  geom_line(size=1.3) +
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  labs(x= "Epoch", y="accuracy", color = "seed", linetype = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))



p = ggplot(mean_more_less_res, aes(x=epoch, y=mean_acc))+
  #geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_more_fewer_answertype100.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
#ggsave("exp2_more_fewer_answertype100.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")
#ggsave("exp3_more_fewer_answertype100.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")


p= ggplot(mean_more_less_res, aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3)+  
  scale_color_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02","#225ea8"))+
  scale_fill_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02", "#225ea8"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_more_fewer_overall100.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp2_more_fewer_overall100.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp3_more_fewer_overall100.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")

# For LESS probe tends to just answer yes a disproportionate amount of times.
# maybe get proportion of yes/no in answers vs predictions
# Also tends to say yes a lot for MORE probe though to a lesser extent.
```

#### MORE - LESS by number difference and overall without zero difference
```{r}

get_more_less_bydiff <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  more_filename = paste(result_dir, "probeMORE_res_by_num_diff.csv", sep="/") 
  less_filename = paste(result_dir, "probeLESS_res_by_num_diff.csv", sep="/")
  more_num_diff <- read_csv(more_filename)
  less_num_diff <- read_csv(less_filename)
  more_less_num_diff <- rbind(more_num_diff, less_num_diff)

  more_less_num_diff_ <- more_less_num_diff |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(probetype, epoch, batchNum, batches, num_diff) |>
    mutate(n_by_diff = sum(counts)) |>
    mutate(correct = ifelse(answer==prediction, "true", "false")) |>
    group_by(probetype, epoch, batchNum, batches, num_diff, correct) |>
    mutate(n_correct_by_diff = sum(counts))

  more_less_num_diff_sum <- more_less_num_diff_ |> 
    filter(correct == "true") |>
    mutate(prop_correct = n_correct_by_diff/n_by_diff) |>
    select(c(probetype, epoch, batches, num_diff, prop_correct)) |>
    unique() |>
    mutate(seed = seed)
  
  return(more_less_num_diff_sum)
}

more_less_diff_res <- result_dirs |> map(get_more_less_bydiff) |> reduce(rbind)

mean_more_less_diff_res <- more_less_diff_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, num_diff) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct))

# by epoch
ggplot(mean_more_less_diff_res, aes(x=epoch, y=mean_acc, color=num_diff))+
  geom_point() +
  scale_colour_gradient2(high = "blue", mid = "yellow", low = "blue") +
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  labs(x= "Epoch", y="Mean accuracy", color = "Distance", fill = "Distance") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

plot_data <- mean_more_less_diff_res |> mutate(num_diff= factor(num_diff, levels = c("-8", "-7", "-6", "-5", "-4", "-3", "-2", "-1", "0", "1", "2", "3", "4", "5", "6", "7", "8"))) 

cols <- c("-8"= "#0D0887FF" , "-7"="#47039FFF", "-6"="#7301A8FF", "-5"="#9C179EFF", "-4"="#BD3786FF", "-3"="#D8576BFF", "-2"="#ED7953FF", "-1"="#FA9E3BFF", "0"="#FDC926FF",
          "1"="#FA9E3BFF", "2"="#ED7953FF", "3"="#D8576BFF", "4"="#BD3786FF", "5"="#9C179EFF", "6"="#7301A8FF", "7"="#47039FFF", "8"="#0D0887FF")

ggplot(plot_data , aes(x=epoch, y=mean_acc, color=num_diff))+
  geom_line(size=1.3) +
  scale_color_manual(values=cols)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  labs(x= "Epoch", y="Mean accuracy", color = "Distance", fill = "Distance") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

plot_data <- mean_more_less_diff_res |> mutate(num_diff= factor(abs(num_diff), levels = c("0", "1", "2", "3", "4", "5", "6", "7", "8"))) |> group_by(probetype, epoch, num_diff) |>
  summarise(mean_acc = mean(mean_acc))

cols <- c("0"="#FDC926FF", "1"="#FA9E3BFF", "2"="#ED7953FF", "3"="#D8576BFF", "4"="#BD3786FF", "5"="#9C179EFF", "6"="#7301A8FF", "7"="#47039FFF", "8"="#0D0887FF")

p = ggplot(plot_data , aes(x=epoch, y=mean_acc, color=num_diff))+
  geom_line(size=1.3) +
  scale_color_manual(values=cols)+
  facet_wrap(vars(probetype), labeller = labeller(probetype = probe.labs))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Absolute difference", fill = "Absolute difference") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_more_fewer_byabsolutedist.jpeg", plot=p, device="jpeg", width = 8.5, height = 3.5, units="in")
#ggsave("exp2_more_fewer_byabsolutedist100.jpeg", plot=p, device="jpeg", width = 8.5, height = 3.5, units="in")
#ggsave("exp3_more_fewer_byabsolutedist100.jpeg", plot=p, device="jpeg", width = 8.5, height = 3.5, units="in")
```

```{r}
## Clearly the num difference is super important and where the model struggles is when there is no difference it says there is almost automatically! This may be because the clevr training set also includes equal_than, similar to more_than/less_than type questions which lead the model to trink that zero difference is a yes answer.

#What is performance like if we remove the zero cases

get_more_less_acc_no0 <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  more_filename = paste(result_dir, "probeMORE_res_by_num_diff.csv", sep="/") 
  less_filename = paste(result_dir, "probeLESS_res_by_num_diff.csv", sep="/")
  more_num_diff <- read_csv(more_filename)
  less_num_diff <- read_csv(less_filename)
  more_less_num_diff <- rbind(more_num_diff, less_num_diff)
  
  more_less_acc_no0 <- more_less_num_diff |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    filter(num_diff != 0) |>
    mutate(correct = ifelse(answer==prediction, "true", "false")) |>
    group_by(probetype, epoch, batchNum, batches) |>
    mutate(n_total = sum(counts)) |>
    group_by(probetype, epoch, batchNum, batches, correct) |>
    mutate(n_correct = sum(counts),
          prop_correct = n_correct/n_total) |>
    ungroup() |>
    filter(correct == "true") |>
    select(probetype, epoch, batchNum, batches, prop_correct) |>
    unique() |>
    mutate(seed = seed)
  
  return(more_less_acc_no0)
}

more_less_res_no0 <- result_dirs |> map(get_more_less_acc_no0) |> reduce(rbind)

mean_more_less_res_no0 <- more_less_res_no0 |> filter(batchNum == 0) |>
  group_by(probetype, epoch) |>
  summarise(mean_acc= mean(prop_correct), sd_acc = sd(prop_correct))


p = ggplot(mean_more_less_res_no0, aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3) +
  scale_color_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02","#225ea8"))+
  scale_fill_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02", "#225ea8"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_more_fewer_overall100_no0.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp2_more_fewer_overall100_no0.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp3_more_fewer_overall_no0.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
```
#### MORE - LESS experiment 3 comparison
```{r}
get_more_less_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  more_filename = paste(result_dir, "probeMORE_res_by_answer_type.csv", sep="/")
  less_filename = paste(result_dir, "probeLESS_res_by_answer_type.csv", sep="/")
  more_acc <- read_csv(more_filename)
  less_acc <- read_csv(less_filename)
  more_less_acc <- rbind(more_acc, less_acc)

  more_less_acc <- more_less_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(probetype, epoch, batchNum) |>
    mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(more_less_acc)
}


# get experiment 1 data
more_less_exp1 <- result_dirs |> map(get_more_less_acc) |> reduce(rbind) |>
  mutate(experiment = "With \"equal\" alternative")

# get experiment 3 data
more_less_exp3 <- result_dirs |> map(get_more_less_acc) |> reduce(rbind) |>
   mutate(experiment = "Without \"equal\" alternative")


more_less_comp <- rbind(more_less_exp1, more_less_exp3)

mean_more_less_comp  <- more_less_comp |> filter(batchNum == 0) |>
  group_by(experiment, probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))

probe.labs <- c("MORE", "FEWER")
names(probe.labs) <- c("probeMORE", "probeLESS")


p= ggplot(mean_more_less_comp, aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3)+  
  facet_wrap(vars(experiment))+
  scale_color_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02","#225ea8"))+
  scale_fill_manual(labels=c("FEWER", "MORE"), values=c("#cc4c02", "#225ea8"))+
  scale_y_continuous(limits=c(0.0, 1.0))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp3_more_fewer_overall100_comp.jpeg", plot=p, device="jpeg", width = 8, height = 3.5, units="in")


```
#### MORE - LESS by number sum
```{r, eval=FALSE}
more_filename = paste(result_dir, "probeMORE_res_by_num_sum.csv", sep="/") 
less_filename = paste(result_dir, "probeLESS_res_by_num_sum.csv", sep="/")
more_num_sum <- read_csv(more_filename)
less_num_sum <- read_csv(less_filename)
more_less_num_sum <- rbind(more_num_sum, less_num_sum)

more_less_num_sum_ <- more_less_num_sum |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
  group_by(probetype, epoch, batchNum, batches, num_sum) |>
  mutate(n_by_sum = sum(counts)) |>
  mutate(correct = ifelse(answer==prediction, "true", "false")) |>
  group_by(probetype, epoch, batchNum, batches, num_sum, correct) |>
  mutate(n_correct_by_sum = sum(counts))

more_less_num_sum_sum <- more_less_num_sum_ |> 
  filter(correct == "true") |>
  mutate(prop_correct = n_correct_by_sum/n_by_sum) |>
  select(c(probetype, epoch, batches, num_sum, prop_correct)) |>
  unique() 

# by batch
ggplot(more_less_num_sum_sum, aes(x=batches, y=prop_correct, color=num_sum))+
  geom_point() +
  facet_wrap(vars(probetype))

# by epoch
ggplot(more_less_num_sum_sum |> filter(batchNum == 0), aes(x=epoch, y=prop_correct, color=num_sum))+
  geom_point() +
  facet_wrap(vars(probetype))
```

#### SAME - NOT SAME (SAME by answer type)
```{r}
get_same_acc <- function(result_dir){
  seed = as.integer(str_sub(result_dir, -1, -1))
  filename = paste(result_dir, "probeSAME_res_by_answer_type.csv", sep="/")
  same_acc <- read_csv(filename)
  same_acc <- same_acc |> mutate(batches = ifelse(batchNum == 0, epoch*10938, (epoch-1)*10938+batchNum)) |> 
    group_by(epoch, batchNum) |>
    mutate(overall_total = sum(n_total), overall_correct = sum(n_correct)) |>
    mutate(seed = seed)
  
  return(same_acc)
}

same_res <- result_dirs |> map(get_same_acc) |> reduce(rbind)

mean_same_res <- same_res |> filter(batchNum == 0) |>
  group_by(probetype, epoch, answer) |>
  summarise(mean_acc = mean(prop_correct), sd_acc = sd(prop_correct), mean_correct= mean(overall_correct/overall_total), sd_correct = sd(overall_correct/overall_total))

# Accuracy by epoch
p= ggplot(mean_same_res, aes(x=epoch, y=mean_acc))+
  geom_ribbon(aes(ymin = (mean_acc - sd_acc), ymax = (mean_acc + sd_acc), fill = answer), alpha=0.3)+
  geom_line(aes(color=answer), size = 1.3)+
  scale_color_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  scale_fill_manual(labels=c("no", "yes"), values=c("#D55E00", "#009E73"))+
  labs(x= "Epoch", y="Mean accuracy", color = "Answer type", fill = "Answer type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_same_answertype_sd.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp1_app_oldsame_answertype_sd.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")

p = ggplot(mean_same_res, aes(x=epoch, y=mean_correct))+
  geom_ribbon(aes(ymin = (mean_correct - sd_correct), ymax = (mean_correct + sd_correct), fill = probetype), alpha=0.3)+
  geom_line(aes(color=probetype), size=1.3)+
  scale_color_manual(labels=c("SAME"), values=c("#225ea8"))+
  scale_fill_manual(labels=c("SAME"), values=c("#225ea8"))+
  labs(x= "Epoch", y="Mean accuracy", color = "Probe type", fill = "Probe type") +
  theme(axis.text = element_text(size=14), legend.text = element_text(size = 14))

p
#ggsave("exp1_same_overall.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
#ggsave("exp1_app_oldsame_overall.jpeg", plot=p, device="jpeg", width = 5.1, height = 3.5, units="in")
# Note the initial peak in accuracy for yes questions is just because the model answers "yes" to the large majority of SAME probe questions indiscriminately
```


